Proposed Solution

### 2016-05-01 CAV/evaluation.tex
config: cav paper fixed some typo

To evaluate our tool, we take a subset of 20 benchmarks from an existsing dataset of configuration errors~\cite{yin11anempirical, configdataset} which are supported by our tool. Table~\ref{table:res} contains an evaluation summary.
We do not report the running times, since they are negligible: even when
 running in the interpreter mode, files are analyzed instantaneously. We spent approximately 30 second on learning the rules. When we run the compiled version, we need for lerning and verification 
combined less than 5 seconds. Our focus is usefulness of the tool: its 
 ability to detect configuration errors and the number of false positives.
 For every benchmark class we took five examples. The middle column represents the number of detected errors, while the right column represents the number of returned false positives per each benchmark.

>>>>

To evaluate our tool, we take a subset of 20 benchmarks from an
existing dataset of configuration errors~\cite{yin11anempirical,xu15hey,configdataset} which are supported by our tool. Table~\ref{table:res} contains an evaluation summary.
We do not report the running times, since they are negligible: even when
 running in the interpreter mode, files are analyzed instantaneously. We
spent approximately 30 second on learning the rules. When we run the
compiled version, we need for learning and verification 
combined less than 5 seconds. Our focus is usefulness of the tool: its 
 ability to detect configuration errors and the number of false positives.
 For every benchmark class we took five examples. The middle column represents the number of detected errors, while the right column represents the number of returned false positives per each benchmark.

### 2016-05-01 CAV/intro1.tex
config: cav paper fixed some typo

Configuration errors are one of the most important root-causes of
modern software system failures~\cite{xu15systems,yin11anempirical}.
In practice, misconfiguration problems may result in security
vulnerabilities, application crashes, severe disruptions in software
functionality, and incorrect program executions%
~\cite{xu15systems,zhang14encore,yuan11context}.  Although several
tools have been proposed to automate configuration error diagnosis
after failures occur~\cite{wang04automatic,attariyan10automating,
su07autobash,whitaker04configuration}, these tools rely on a manual approach
  to understand and detect the failure symptoms. The main reasons for this are:
  1) entries in configuration files are untyped assignments, 2) there
  is no explicit structure policy for the entries in configuration
  files, and 3) there are surprisingly few rules specifying the
  entries' constraints.

@@

Finally, from a systems perspective this is the first approach that {\emph{proactively}} checks 
 the correctness of configuration files. All previous work
~\cite{xu15systems,zhang14encore,yuan11context, wang04automatic,attariyan10automating,
su07autobash,whitaker04configuration} tries to identify the problem after the
failure occured. Our approach isolates potential errors before the system failure occurs, e.g. before the installation. We can also see \app as a tool that can run in conjunction with existing tools. Pre-analyzed configuration files are already free from language-based errors, and this way the workloads of post-failure forensics at the runtime
is significantly reduced, thus making these tools truly practical.

>>>>

Configuration errors are one of the most important root-causes of
modern software system failures~\cite{xu15systems,yin11anempirical}.
In practice, misconfiguration problems may result in security
vulnerabilities, application crashes, severe disruptions in software
functionality, and incorrect program executions%
~\cite{xu15systems,xu13do,zhang14encore,yuan11context}.  Although several
tools have been proposed to automate configuration error diagnosis
after failures occur~\cite{wang04automatic,attariyan10automating,
su07autobash,whitaker04configuration}, these tools rely on a manual approach
  to understand and detect the failure symptoms. The main reasons for this are:
  1) entries in configuration files are untyped assignments, 2) there
  is no explicit structure policy for the entries in configuration
  files, and 3) there are surprisingly few rules specifying the
  entries' constraints.

@@

Finally, from a systems perspective this is the first approach 
that {\emph{proactively}} checks 
 the correctness of configuration files. All previous work
~\cite{xu15systems,zhang14encore,yuan11context, wang04automatic,attariyan10automating,
su07autobash,whitaker04configuration} tries to identify the problem after the
failure occurred. Our approach isolates potential errors before the system failure occurs, e.g. before the installation. We can also see \app as a tool that can run in conjunction with existing tools. Pre-analyzed configuration files are already free from language-based errors, and this way the workloads of post-failure forensics at the runtime
is significantly reduced, thus making these tools truly practical.

### 2016-05-01 CAV/motiv1.tex
make a new dir for icfp
config: cav paper fixed some typo

When writing configuration files, users usually take already existing
files and modifies the files, with little knowledge of the system. 
The non-expert user can then easily introduce in errors.
Even worse, the original file may already corrupted and the errors are propagated further. 
Below we show some real worlds examples of the errors commonly found in configuration files.
All these examples are extracted from real-world reports % ~\cite{yin11anempirical, configdataset}.
The deep, domain specific knowledge needed to identify these error manually is strong motivation for a tool such as \app.

>>>>

When writing configuration files, users usually take already existing
files and modify the files, with little knowledge of the system. 
The non-expert user can then easily introduce in errors.
Even worse, the original file may already corrupted and the errors are propagated further. 
Below we show some real worlds examples of the errors commonly found in configuration files.
All these examples are extracted from real-world reports%
~\cite{yin11anempirical,xu15hey}.
The deep, domain specific knowledge needed to identify these error manually is strong motivation for a tool such as \app.
